---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# metamedian

The goal of metamedian is to provide a method of estimating the approximate variance of the sample median provided with summary statistics.

The function takes the arguments sample size $n$, along with sample summary statistics taken from one of the following sets: $C_1 := \{a, m, b\}$, $C_2 := \{q_1, m, q_3 \}$, or $C_3 := \{a, q_1, m, q_3, b\}$.

From these known sample summary statistics, the variance of the sample median is estimated.

This package will also include the analysis and comparison with existing estimators.

## Installation

You can install metamedian from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("softloud/metamedian")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
## basic example code
```
