<!-- 
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Single study data} 
-->
---
title: "Single-study data"
author: "Charles T. Gray"
date: `r dontpanic::title_date()`
vignette: >
  %\VignetteIndexEntry{Single study data generations}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

rm(list = ls())

```

## Tasks

- Plot distributions.

## Set number of trials

```{r Set trials}
trials <- 10 # For testing.
# trials <- 1000 

```

## Set distributions

We want to generate summary statistics from various distributions.

```{r Set distributions}
# Create a tibble with a variable for distribution and one for parameters. Since parameters have varying lengths and names, it will be a list object.

distributions <- tibble(
  rdist = character(),
  rpar1 = list()
) 

# Add distributions with one parameter.
distributions <- distributions %>% 
  add_row(rdist = "exp",
          rpar1 = 1)

# Add distributions with two parameters.
distributions <- distributions %>% 
  mutate(rpar2 = list(rep(NULL, nrow(distributions)))) %>% 
  add_row(rdist = "norm",
          rpar1 =  50,
          rpar2 = 17)

# Take a look.
distributions %>% knitr::kable()
```

```{r Write distributions to package}
devtools::use_data(distributions, overwrite = TRUE)

```

### See distributions

```{r See distributions}
see_dist <- function(rdist = "lnorm", pars = c(2, 1)) {
  # ToDo: Create plotting function.
}

```


### Add sample sizes

```{r Set samples sizes.}
sample_sizes <- c(15, 60, 100)

devtools::use_data(sample_sizes, overwrite = TRUE)

ss_data <- distributions %>% 
  mutate(n = sample_sizes[1])

i <- 2

while (i < length(sample_sizes)) {
  ss_data <- rbind(ss_data,
                   distributions %>% 
                     mutate(n = sample_sizes[i]))
  i <- i + 1
}

# Take a look.
distributions %>% knitr::kable()

```

##  Generate trials

```{r Generate trials dataset}
ss_data <- tibble(
  rdist = rep(ss_data$rdist, each = trials),
  rpar1 = rep(ss_data$rpar1, each = trials),
  rpar2 = rep(ss_data$rpar2, each = trials),
  n = rep(ss_data$n, each = trials)
)

```

# Generate samples

```{r Generate samples}
ss_data <- ss_data %>%
  mutate(sample = pmap(
    .l = list(rdist,
              rpar1,
              rpar2,
              n),
    .f = function(rdist, rpar1, rpar2, n) {
      dontpanic::get_sample(n = n,
                            dist = rdist,
                            par = c(rpar1, rpar2))
    }
  ))

```

# Calculate summary statistics

```{r Summary statistics}
ss_data <- ss_data %>% 
  mutate(
    min = map_dbl(sample, min),
    first_q = map_dbl(sample, quantile, probs = 0.25),
    median = map_dbl(sample, median),
    third_q = map_dbl(sample, quantile, probs = 0.75),
    max = map_dbl(sample, max),
    iqr = third_q - first_q,
    mean = map_dbl(sample, mean),
    sd = map_dbl(sample, sd)
  ) %>% # Remove samples variable to reduce bulk. 
  select(-sample)

```

```{r Write ss data to package}
devtools::use_data(ss_data, overwrite = TRUE)
```

