<!-- 
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Single study data generation} 
-->
---
title: "Single-study data"
author: "Charles T. Gray"
date: `r dontpanic::title_date()`
vignette: >
  %\VignetteIndexEntry{Single study data generation}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(metamean)

rm(list = ls())

```

## Tasks

- Plot distributions.
- Rewrite open with `purrr::cross`; it's going to drive me crazy until I do. 
- Document all datasets stored using `use_data` in this sheet.

## Set number of trials

```{r Set trials}
trials <- 10 # For testing.
# trials <- 1000 

```

# Generate data

We want to generate summary statistics of samples drawn from various distributions.

## Set distributions

```{r Set distributions}
distributions <- list(
  list(rdist = "norm",
       rpars = list(mean = 50, sd = 17)),
  list(rdist = "lnorm",
       rpars = list(meanlog = 4, meansd = 0.3)),
  list(rdist = "beta",
       rpars = list(9, 4)),
  list(rdist = "exp",
       rpars = 10),
  list(rdist = "weibull",
       rpars = c(2, 35))
  list(
    rdist = "lnorm",
    rpars = list(meanlog = 1, sdlog = 0.25)
  )
  # list(
  #   rdist = "lnorm",
  #   rpars = list(meanlog = 1.1, sdlog = 0.25)
  # ),
  # list(
  #   rdist = "lnorm",
  #   rpars = list(meanlog = 1, sdlog = 0.5)
  # ),
  # list(
  #   rdist = "lnorm",
  #   rpars = list(meanlog = 1.1, sdlog = 0.5)
  # ),
  # list(
  #   rdist = "exp",
  #   rpars = list(rate = 1)
  # ),
  # list(
  #   rdist = "exp",
  #   rpars = list(rate = 1.1)
  # ),
  # list(
  #   rdist = "exp",
  #   rpars = list(rate = 1.5)
  # ),
  # list(
  #   rdist = "exp",
  #   rpars = list(rate = 2)
  # ),
  # list(
  #   rdist = "chisq",
  #   rpars = list(df = 1)
  # ),
  # list(
  #   rdist = "chisq",
  #   rpars = list(df = 1.1)
  # ),
  # list(
  #   rdist = "chisq",
  #   rpars = list(df = 4)
  # ),
  # list(
  #   rdist = "chisq",
  #   rpars = list(df = 4.1)
  # ),
  # list(
  #   rdist = "beta",
  #   rpars = list(shape1 = 10, shape2 = 10)  
  #   ),
  # list(
  #   rdist = "beta",
  #   rpars = list(shape1 = 10.1, shape2 = 10)
  # ),
  # list(
  #   rdist = "weibull",
  #   rpars = list(shape = 1, scale = 1)
  # ),
  # list(
  #   rdist = "weibull",
  #   rpars = list(shape = 1.1, scale = 1)
  # ),
  # list(
  #   rdist = "weibull",
  #   rpars = list(shape = 2, scale = 1)
  # ),
  # list(
  #   rdist = "weibull",
  #   rpars = list(shape = 2.1, scale = 1)
  # ),
  # list(
  #   rdist = "weibull",
  #   rpars = list(shape = 10, scale = 1)
  # ),
  # list(
  #   rdist = "weibull",
  #   rpars = list(shape = 10.1, scale = 1)
  # ),
  # list(
  #   rdist = "norm",
  #   rpars = list(mean = 3, sd = 1)
  # ),
  # list(
  #   rdist = "norm",
  #   rpars = list(mean = 1, sd = 0.2)
  # ),
  # list(
  #   rdist = "norm",
  #   rpars = list(mean = 1.1, sd = 0.2)
  # ),
  # list(
  #   rdist = "gamma",
  #   rpars = list(shape = 5, rate = 1)
  # ),
  # list(
  #   rdist = "gamma",
  #   rpars = list(shape = 5.1, rate = 1)
  # ),
  #   list( # Can't calculate sd for cauchy.
  #   rdist = "cauchy",
  #   rpars = list(location = 2, scale = 0.5)
  # ),
  #   list(
  #   rdist = "cauchy",
  #   rpars = list(location = 2, scale = 1)
  # )
)



```

## Create trials

```{r Set parameters}
# Set parameter sets.
ss_data <- cross(list(
  trial = seq(1, trials),
  n = c(15, 60, 100),
  distributions = distributions
))

```


```bcv h
# Initialise simulation tibble.
ss_data <- tibble(
  rdist = map_chr(ss_data, c("distributions", "rdist")),
  rpars = map(ss_data, c("distributions", "rpars")),
  n = map_dbl(ss_data, "n"),
  trial = map_int(ss_data, "trial")
) %>%
  mutate(true_median = # Calculate true median.
           pmap_dbl(
    list(dist = rdist, par = rpars),
    .f = dontpanic::any_dist,
    x = 0.5
  ), # Create adjustment on first parameter for different arms.
  rpar1_adj = map_dbl(rpars, 1) + 0.1,
  rpar1 = map_dbl(rpars, 1),
  rpar2 = map(rpars, 2),
  true_mean = map2_dbl(rdist, rpars, dontpanic::get_mean)
  )

```

### Check that every row is distinct

```{r }
ss_data %>% distinct() %>% nrow() == nrow(ss_data)
```

```{r}
ss_data %>% 
  count(rdist, as.character(rpars), n) %>% 
  filter(nn != 10)
```


### Create zero-$\Delta$ and non-zero-$\Delta$ adjustment

```{r Adjustment}
nrows_ss_data <- ss_data %>% nrow()

ss_data <- ss_data %>% 
  mutate(gather_arg = rpar1) %>% 
  gather(key = "adj_status",
         value = "rpar1_arm2",
         gather_arg, rpar1_adj) 

# Check that I've doubled the number of observations.

ss_data %>% nrow() == nrows_ss_data * 2
```

```{r}

ss_data %>% 
  count(rdist, as.character(rpars), n, adj_status) %>% 
  filter(nn != 10)


```


## Generate samples

```{r Generate samples}
ss_data <- ss_data %>%
  mutate(sample_1 = pmap(
    .l = list(rdist,
              rpar1,
              rpar2,
              n),
    .f = function(rdist, rpar1, rpar2, n) {
      dontpanic::get_sample(n = n,
                            dist = rdist,
                            par = c(rpar1, rpar2))
    }
  ),
  sample_2 = pmap(
    .l = list(rdist,
              rpar1_arm2,
              rpar2,
              n),
    .f = function(rdist, rpar1_arm2, rpar2, n) {
      dontpanic::get_sample(n = n,
                            dist = rdist,
                            par = c(rpar1_arm2, rpar2))
    }
  )
  )

```


```{r}

ss_data %>% 
  count(rdist, as.character(rpars), n, adj_status) %>% 
  filter(nn != 10) %>% nrow()


```


# Calculate summary statistics

```{r Summary statistics}
# Function to produce a summary tibble from a sample.
sample_summary <- function(sample) {
  tibble(
    min = min(sample),
    first_q = quantile(sample, probs = 0.25),
    median = median(sample),
    third_q = quantile(sample, probs = 0.75),
    max = max(sample),
    mean = mean(sample),
    sd = sd(sample),
    n = length(sample)
  ) %>%
    mutate(iqr = third_q - first_q)
}

# Create summary variables for both arms.
ss_data <- ss_data %>%
  mutate(
    sample_stats_1 = map(sample_1, sample_summary),
    sample_stats_2 = map(sample_2, sample_summary)) %>%
  select(-sample_1,-sample_2)

```


```{r}

ss_data %>% 
  count(rdist, as.character(rpars), n, adj_status) %>% 
  filter(nn != 10) %>% nrow()


```

```{r Write ss data to package}
ss_par <- list(
  distributions,
  trials 
)

devtools::use_data(ss_par, overwrite = TRUE)
devtools::use_data(ss_data, overwrite = TRUE)
```


