<!-- 
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Single study data} 
-->
---
title: "Single-study data"
author: "Charles T. Gray"
date: `r dontpanic::title_date()`
vignette: >
  %\VignetteIndexEntry{Single study data generations}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(metamean)

rm(list = ls())

```

## Tasks

- Plot distributions.
- Rewrite open with `purrr::cross`; it's going to drive me crazy until I do. 
- Document all datasets stored using `use_data` in this sheet.

## Set number of trials

```{r Set trials}
trials <- 10 # For testing.
# trials <- 1000 

```

# Generate data

We want to generate summary statistics of samples drawn from various distributions.

## Set distributions

```{r}
distributions <- list(
  list(rdist = "norm",
       rpars = list(mean = 50, sd = 17)),
  list(rdist = "lnorm",
       rpars = list(meanlog = 4, meansd = 0.3)),
  list(rdist = "beta",
       rpars = list(9, 4)),
  list(rdist = "exp",
       rpars = 10),
  list(rdist = "weibull",
       rpars = c(2, 35))
) 
```

## Create trials

```{r}
# Set parameter sets.
ss_data <- cross(list(
  trial = seq(1, trials),
  n = c(15, 60, 100),
  distributions = distributions
))

```


```{r Generated data}
# Initialise simulation tibble.
ss_data <- tibble(
  rdist = map_chr(ss_data, c("distributions", "rdist")),
  rpars = map(ss_data, c("distributions", "rpars")),
  n = map(ss_data, "n")
) %>%
  mutate(true_median = # Calculate true median.
           pmap_dbl(
    list(dist = rdist, par = rpars),
    .f = dontpanic::any_dist,
    x = 0.5
  ), # Create adjustment on first parameter for different arms.
  rpar1_adj = map_dbl(rpars, 1) + map_dbl(rpars, 1) / 2,
  rpar1 = map_dbl(rpars, 1),
  rpar2 = map(rpars, 2)
  )

```

## Generate samples

```{r Generate samples}
ss_data <- ss_data %>%
  mutate(sample_1 = pmap(
    .l = list(rdist,
              rpar1,
              rpar2,
              n),
    .f = function(rdist, rpar1, rpar2, n) {
      dontpanic::get_sample(n = n,
                            dist = rdist,
                            par = c(rpar1, rpar2))
    }
  ),
  sample_2_adj = pmap(
    .l = list(rdist,
              rpar1_adj,
              rpar2,
              n),
    .f = function(rdist, rpar1_adj, rpar2, n) {
      dontpanic::get_sample(n = n,
                            dist = rdist,
                            par = c(rpar1_adj, rpar2))
    }
  ),
    sample_2_null = pmap(
    .l = list(rdist,
              rpar1,
              rpar2,
              n),
    .f = function(rdist, rpar1, rpar2, n) {
      dontpanic::get_sample(n = n,
                            dist = rdist,
                            par = c(rpar1, rpar2))
    }
  )
  )

```

# Calculate summary statistics

```{r Summary statistics}
# Function to produce a summary tibble from a sample.
sample_summary <- function(sample) {
  tibble(
    min = min(sample),
    first_q = quantile(sample, probs = 0.25),
    median = median(sample),
    third_q = quantile(sample, probs = 0.75),
    max = max(sample),
    mean = mean(sample),
    sd = sd(sample),
    n = length(sample)
  ) %>%
    mutate(iqr = third_q - first_q)
}

# Create summary variables for both arms.
ss_data <- ss_data %>%
  mutate(
    sample_stats_1 = map(sample_1, sample_summary),
    sample_stats_2_null = map(sample_2_null, sample_summary),
    sample_stats_2_adj = map(sample_2_adj, sample_summary)
  ) %>%
  select(-sample_1,-sample_2_null,-sample_2_adj)

```

```{r Gather}
ss_data <- ss_data %>% 
  gather(key = "arm_adj",
         value = "sample_stats_2",
         sample_stats_2_adj, sample_stats_2_null)
```


```{r Write ss data to package}
ss_par <- list(
  distributions,
  trials 
)

devtools::use_data(ss_par, overwrite = TRUE)
devtools::use_data(ss_data, overwrite = TRUE)
```

